\chapter{Examples of the Real Data}\label{app:A}
Here we present the examples of texts and their respective summaries. Original texts are presented and may include profanities or offensive language.

\textbf{Post title:} Why should any American company ever act responsibly again?

\textbf{Original text:} Whats the point of good corporate governance and fiscal responsibility? The companies that leveraged themselves to the moon, did stock buybacks to hyper-inflate their stock price, live on constant debt instead of good balance sheets are now being bailed out by unlimited QE. Free money to cover your mistakes. Why would anyone run a good business ever again? Just cheat and scheme and get bailed out later.

Edit: I am truly honored to be the number 1 post on WSB. To get validation from you autists and retards, the greatest American generation, is the peak moment of my life. Thank you all.

Edit 2: Many of you are saying this post is socialist. It is anti-capitalist. It is anti-wall street. It is none of that. My post is in fact about fixing capitalism so it is done the right way. Don’t reward companies that are managed poorly and don’t invest their profits wisely. Capitalism is about survival of the fittest and rewarding the winners not the schemers and cheaters. I’d rather have a profitable company that pays its workers livable wages, doesn’t use sweat shop labor, doesn’t pollute our environment, gives good quality healthcare, paid family leave, sick leave, maternity/paternity leave, reinvests in improving infrastructure, keeps low debt to equity, and has a 12 month emergency fund for a black swan event. Not companies that give all the money to the CEO and Board and nothing to the workers, do stock buy-backs with profits instead of improving infrastructure or saving for emergency funds. Let the greedy poorly run companies fail so we can invest only in good quality companies that treat their workers well. We will all make tons of profits in the market with well run companies and main street America will also be able to live a decent quality life.

Edit 3: I am not a salty bear. In fact I want the market to do well. But this is not the way. Bailing out weak companies that didn’t save for a black swan event because of CEO greed is just making this bubble bigger and bigger and it will only pop worse later on.

JPow will ruin our market and the economy with this fake bubble with his printer. Let the market be free so we can shed weak companies and true capitalism can see a rise of the strong companies and the market can moon again. JPow and his printer are really helping the Wall street elite. Jpow doesn’t care about you. Now the tax payers are bailing out shadow banking. Junk bonds are risky loans that private equity, hedge funds, and other shadow banking institutions give out to desperate companies that can’t get loans from regular banks anymore. That’s why junk bonds are shadow banking instead of traditional banking. JPow is using his unlimited printer to BAILOUT and give free money to the shadiest and greediest characters of wall street and society in general -- private equity, hedge fund managers, shady billionaires.

PE, hedgies, shady billionaires were screwed because the economy just halted and companies were going to default on these risky loans since they had no revenue coming in. This is who JPow is helping. He just bailed them all out by buying these risky junk bonds on the back of the American tax payer. You may become homeless and starve, but private equity, hedge fund managers, and shady billionaires will be made whole by the fed.

\textbf{Post summary:} I hate the market, and I don’t think we need to talk to each other.

\textbf{Comments summary:} Every company’s goal should be to become ‘too big to fail’ with enough employees to be worth bailing out.

\textbf{Post title:} People are risking their lives to wage war against the suits and it brings tears to my eyes to watch them do it.

\textbf{Original text:} That is not hyperbole. Money isn’t just paper used to buy cocaine and hookers. It is a physical representation of a portion of a man’s life. Make 50,000 a year in a soul sucking desk job? Taking a 50,000 position on GME is risking a year off your life to fight this good fight. The amount of years so many of you are willing to put on the line is an amazing testament to how dedicated this sub is to fucking these bastards raw. The bastards who steal thousands of years off the regular man’s lives every single day. You’re fighting the good fight, and your sacrifices will not be forgotten.

\textbf{Post summary:} The bastards who steal thousands of years off the regular man’s lives every single day.

\textbf{Comments summary:} I don’t know how to get a job, but I think that’s why I hate the fuck out of it.

\textbf{Post title:} I Pledge to Delete Robin Hood After The Great Rise. Who’s With Me?

\textbf{Original text}: Let’s show them how many of their traders are out. These fuckers are set to IPO this year, fools. Who’s trading data are you gonna sell if all of us leave? Shilling out to big money was the worst financial mistake of your pathetic wanna-be corps life. I’m out, but I’m not selling on RH until it’s motherfucking done. Collect tendies and your tax information and split. Who’s with me?

GME 5000 is not a meme.

I am not a financial advisor

\textbf{Post summary:} There are a lot of factors out there. It’s not a meme.

\textbf{Comments summary:} The market is not as bad as you think. These examples demonstrate three types of summaries: entirely new text in the first example, a line from the original post (resulting in summary, common for extractive approach) and combination of words from original post with new ones.

\chapter{Appendix}\label{app:B}

\begin{longtblr}[
	]{
		colspec = {XXXXX}, 
		width = 1.0\linewidth,
		rowhead = 1,
	} 
	\toprule
	Topic & Topic words & Subtopic time interval & Number of posts for summarization & Text\\
	\hline
	0 & Climate Change Republican State & 03.07--24.11 & 300 & The narrator continues his argument against climate change in this chapter, explaining that the evidence is overwhelming and that it would be impossible to deny it completely. He then discusses Biden\' campaign for President of the United States on climate change. On Day 4, the "reality TV challenge" comes up with new challenges for Biden: whether it\'s Poilieve or Jean Charrest, climate change can sink the next conservative leader. If someone does don\'t want to believe there\'s definite proof, what irrefietable proof would they offer them to alter their opinion? In other words, no one will tell him about the climate change statistics. Even though Biden has already proposed a law making it illegal for rich men to set fires to add particulates to the air, people are still not willing to admit that they have been wrong all along. Finally, on Day 4, Gore announces that Congress must make peace with climate change before the midterm elections.\\
	\hline
	1 & Dont Like Want Feel & 03.07--24.11 & 50 & The narrator describes his life as Chaos, and the world is chaos. He has no passions or ambitions but wants to disappear. His brother probably will die soon because it's so badly treated. He hates everything. He doesn't know where to go from here. He can't find peace in anyone to love. He feels like he's already reached the end of his rope. He knows that society is going to get worse when climate change destroys civilization. He also realizes that people have been much better off than him since he started studying law. He thinks about suicide too. He does not want to be alone anymore. He just hates himself for being trapped in existence with all this bad news. He wishes he could live on a good note and on his own terms. He asks anyone else who is going through similar problems. They say that they are crippled with mental issues, lack of work, and one friend whom they talk to every month. She tells him that her best friend plans to have another child. She says that she would rather have four kids than five. She adds that there is only one problem: most families have two working mothers. She wants to speak to my friend more directly. She hopes that he regrets his behavior by coming across as means.\\
	\hline
	2 & Climate Change Fight Hellscapes & 03.07--24.11 & 300 & In this chapter, the narrator explains how people can come together and fight climate change better for less money. He also discusses some of the most important threats to humankind: penguins being threatened by climate change; giant cities becoming uninhabited; and so on. He asks what people can do to make it easier for them to stop climatechange. Some of the best known examples are from the book "In which Carbon Emissions Threaten Methane" by Professor Carl-Octavius Otto Weiss. These include making methane more powerful in the atmosphere than expected, using burning it on fire as a way to slow climate change, creating penguin colonies that are at risk of extinct because of climate change\'s influence, and even forcing humans to use electricity to help control the climate. The worst scenario would be for people to delay action until they could no longer live in their own communities. People would start investing more into climate change immediately, leaving the mass of people hungry and thirsty. There would be political will and companies would invest more into fighting climate change. Finally, there would be an end to the world\'s current cycle of heat and cooling. This is why we have to go underground and build a nuclear winter on the planet.\\
	\hline
	3 & change climate canada greener & 03.07--24.11 & 700 & In this chapter, Sebastian Vettel explains how climate change is making his life easier. He says that the Alberta Oil Sands are one of the most harmful places in the world because you can chop down trees and destroy them just to extract oils. Then he tells us that it's up to everyone in the Ontarian community to fight against climate change. They're all going to file lawsuits against the government for failing to reduce their greenhouse gas footprints by cutting back on energy-consuming businesses. We learn that five young people will sue the government over an international treaty that allows oil-industry companies to sue governments for taking action toward climate change; they're also going to get some new statistics about how much each of these measures has saved Canada. It's clear that there's no way anyone could be more concerned about climate change than the seven young men who are suing the federal government.\\
	\hline
	\SetCell[r=3]{m}{4} & Government Party Ontario Australia & 03.07--06.07 & 50 & In this chapter, the author discusses the recent actions taken by the new government in Australia on climate change and how it will affect the country's economy. He also discusses Jaimie Macevoy's run for city council as well as other issues that are important to the community. The state government has slain many of its public board members, including returning to work with an executive named Greg McCarthy. A number of political parties have formed boards to advise governments on issues such as poverty, climate change, corruption, and violence against women. Some candidates have already been elected, but others have not yet been appointed. This list includes some of the most damaging decisions made by the current government.\\
	
	& Government Climate Change People & 06.07--30.07 & 50 & The party launches its election campaign in North Shore with a crowd of supporters. Pacman, the party\'s leader, delivers a long speech about how his party is committed to "unlocking New Zealand\'s potential economically and culturally." He says that the government\'s budget has failed to address many of the issues New Zealand faces, including housing, crime, and the environment. He also points out that the Prime Minister refused to answer many questions during his term as Minister for Mori or Pasifika affairs. He tells the crowd that he was proud of his record answering these questions but that this failed government had never given to the people\'s elected representatives on any occasion. He adds that it needs a road to net zero to secure the climate change authority and measures for proper national conversation.\\

	& Like Life Kids People & 30.07--24.11 & 50 & Australia's House of Parliament has passed a bill to reduce its greenhouse gas by 43 percent below the 2005 level by 2030. The Green Party supports the bill, but the conservatives are not ready to move from the Paris commitment to cut climate change by 28 percent to 35 percent. In addition to this new legislation, the government will introduce measures to improve the nation's transportation system and create new jobs. He will also make sure that Australia is able to thrive for all future generations. His government will invest in new roads, railways, air forces, and cybersecurity. He plans to build new national parks, oceanic parks, anti-piracy summits, and other measures to help slow and perhaps reverse the damage caused by climate change. He promises to replace the ban on gas cars by twenty-five with a better plan to phaseout gas cars. This will be an important step towards reducing climate change because it will save us from rising sea levels.\\
	\hline
	5 & Food Change Climate Farmers & 03.07--24.11 & 150 & The narrator discusses the latest developments in food production and politics. He uses examples from the Netherlands, India, and Africa to explain how climate change is affecting food supply chains. He also addresses concerns about food prices in the U. S. as well as issues of poverty and hunger in Africa. He suggests that farmers can use genetically modified plants to help combat climate change.\\
	\hline
	\SetCell[r=2]{m}{6} & India Heat Climate Change & 03.07--21.08 & 100 & In this chapter, the narrator explains how India\'s actions toward the climate crisis have been misunderstood. He asks whether anyone can explain why India is making such a fuss over the topic of climate change and what it means to be an active citizen in the future. The narrators discuss several topics: 1) Heatwaves; 2) Climate Change; 3) India; and 4) Composting. They also discuss the role of Medha Patker, one of the pioneers of the "Narada BhaoAndolan" movement against the Sardar Saraovar Dam project in India.\\
	
	& Climate Change India Energy Renewable & 21.08--24.11 & 100 & In this chapter, the author explains how India is planning to use deep sea cables to create a green electricity grid as well as reduce its energy consumption by up to 45\%. He also discusses some of the latest developments in the Indian business community. For example, there are plans to build an underseal cable linking the Gujarat coast with the Middle East and creating a new renewable energy Grid as India and Arab Arabia. The article also mentions that Prince Abdul Aziz Bin Salman will be visiting New Delhi next month for a visit. Also, it\'s announced that India has already received invites from the Sultan of Salman to New Delhi. This makes the reader wonder whether climate change will hit much more often than it does now. According to one of the most recent reports on India\'s economic loss due to heat waves, India lost about 159 Billion in key sectors because of extreme heat stress. If temperatures increase by a certain amount, labor hours will decline by 53\%; snowfall will increase by 3 times that expected at a temperature of 1.4 deg. Heatwaves are increasing frequency and temperature across Europe. Meanwhile, India has set up a council on climate change called the "Climate Change Council" to discuss ways to combat climate change. There are many opportunities to attend the council: you can speak as a delegate or speaker; you can attend as part of a session; you may participate as if you were a speaker; etc.\\
	\hline
	\SetCell[r=2]{m}{7} & Protest Climate Chnage Wilson & 03.07--06.07 & 100 & In this short scene, the narrator explains how climate change protests are taking place in Sydney. He describes how an old lady dressed as an elderly woman throws a cake at Mona Lisa\'s painting and then throws roses at her. This is not a typical example of what happens when people try to raise awareness about a political issue. It\'s more like "raising awareness" for money than for anything else. The man dressed up as an older woman yells that it\'s all about climate change. A bunch of people have been arrested for blocking roads or highways because they\'re passionate about something. They don\'t want to get into trouble with big-time politicians who just want to make money. But there\'s no way anyone can do anything about such a thing. So here\'s some background on why: People tend to block roads when they\'ve got a passion for something. If you\'re going to advocate for something, you need to be willing to go against it. You know, things like voting for better urban planning, public transport, etc. And so forth. There\'s nothing wrong with these kinds of actions.\\
	
	& Rainn Name Wilson Chnages & 06.07--24.11 & 150 & Rainn Wilson has changed his name to Protest climate change, and he\'s been getting more and more public attention for the past few weeks. He changes his name from "Rainnahfall Heatwave Extreme Winter" to "Protestclimate Change." And then he announces that he is changing his name so that people can see him as an advocate for climate change. So what does this mean? Well, it doesn\'t seem like there\'s much of a difference between throwing soup over Vangogh\' painting or throwing food at a famous paintings. The whole thing is just trying to get people to stop using oil in their lives. They are also spreading hate on reddit because they don\'t want to be seen as supporting the cause. In other words, they\'re not helping anyone but themselves.\\
	\hline
	\SetCell[r=2]{m}{8} & School Environmen Climate Change Science & 03.07--12.09 & 50 & The top program for a student to study "climate change" requires a personal statement and an essay explaining how the degree will help him achieve his future goals. This is important because it allows students to tell their stories and explain what they have experienced in their lives. In this case, she has a background of studying "econ" and "math." She wants to be able to combine her passion for science with her desire to fight climate change. She\'s been working as a tech salesman since February 20, 2021 so she doesn\'t need a job but wants to do something meaningful. She knows that she can get into a graduate school where she can focus on helping people make better decisions about climate change while also getting a high paying job. Her biggest ambition is to become an economic analyst or consultant in any industry or local government. She needs experience in managing large scale projects like climate change and would like to work at a consulting company doing business research. She does not know how to write her personal statement; instead, she just wants to talk about why she wants to go to college. She had a hard time taking math classes due to lack of commitment. She wanted to pursue econ studies but didn\'t really want to finish them all. She was worried about having enough motivation to complete these courses when she got bad grades. Finally, she decided to try to apply to university after graduating from UW. She started looking for jobs outside of medicine and found some opportunities in finance. She tried to find career advice by asking other students who had taken a Geography or Earth Science degree. They were all very different. Some said that earth sciences and geography seemed more respected than other fields, but others said that law wasn\'t as respected as many other fields. Isn\'t there anything else you could do? If you are interested in finding out what kind of degree you should take, please feel free to ask.\\

	& School Year Climate Would Change & 12.09--24.11 & 30 & Engineering is the best career choice for high school students because it\'s about creating revolutionary inventions to benefit humanity. There are plenty of top engineering jobs available in India, including aerospace engineers, chemical engineers, and nuclear engineers. The fields of civil engineering, transportation engineering, and environmental engineering are also popular among those who love thinking outside the box - they can get international opportunities.\\
	\hline
	\SetCell[r=2]{m}{9} & Floods Pakistan Flooding Climate & 03.07--10.07  & 100 & The narrator discusses how climate change is making floods worse in the country. He says that there are more record- breaking records in the world because of it. A huge fire broke out at Islamabad on Tuesday, and the authorities rushed to rescue people from the affected area. The Prime Minister has instructed the capital development authority to forestall the fire immediately. In this chapter, the author describes some of the major disasters that have occurred since June 14, including an earthquake in India; a monoon storm in Bangladesh; and a series of floods in China. Sherry reports that many people have died due to the heavy rains. According to her, "This is one national disaster." As many as seven people have lost their lives in recent rain-retrieval incidents across the country," Rehman tells the nation\'s chief minister, saying that this is a "national disaster." Since June 14, Monsoneon storms have killed about 77 people in Pakistan. This is not considered a big threat to the country but rather a challenge for its citizens. Climate change makes flooding worse.\\

	& Floods Pakistan Flooding Climate & 10.07--24.11 & 150 & The narrator discusses the recent heavy rains and floods in South Korea, Nigeria, Chad, and other countries. He says that climate change likely caused deadly floods because of its effects on the environment. A report finds that one third of Pakistan\'s population is under water due to ancient flooding. Sherrie Rehman tells the AFP that she could make a "third of country underwater" by changing the climate. The government of Pakistan asks for help from the international donor community as it faces high inflation and an overconfident current account deficit. In response, the United States has pledged \$139 million to help people affected by the disaster. As part of this commitment, the Azgartesy charity will donate more than \$1 million to support relief efforts across the country through local, vetoed organizations.\\
	\bottomrule
\end{longtblr}